\mytitle{}

### 2018-11-06 paper/paper.tex
Improvements to table script, paper.

\usepackage[binary-units, per-mode=symbol]{siunitx}
\sisetup{detect-all, range-phrase=--, range-units=single}

@@

@@

{
\newcommand{\load}[2]{\operatorname{load}^{#2}_{t}(#1)}
\newcommand{\uload}[1]{\load{#1}{\uparrow}}
\newcommand{\dload}[1]{\load{#1}{\downarrow}}
\newcommand{\bload}[1]{\load{#1}{\updownarrow}}
\newcommand{\cond}[2]{\operatorname{c}_{#1,t}#2}
%\fakepara{Reward function directionality}
The reward functions, as defined, do not take traffic direction into account.
We redefine these to identify overload states using both upstream and downstream loads, while allowing customisation of which direction is chosen for protection.
Denoting the upstream, downstream and combined loads $\uload{s}, \dload{s}, \bload{s}$, we modify \cref{eqn:reward}:
\begin{subequations}
\begin{gather}
\cond{f} = [\max(\uload{s}, \dload{s}) > U_s],\\
\cond{c}{(v)} = \cond{f}{} \cdot{} \, [\max(\uload{l_v}, \dload{l_v}) > U_s/k],
\end{gather}
\label{eqn:reward-but-better}
\end{subequations}
replacing $\load{t}{}$ in \crefrange{eqn:reward-rt}{eqn:reward-rctl} with whichever directional load is prioritised.
We choose $\uload{\cdot}$ for our UDP-based models and $\dload{\cdot}$ for HTTP, though we expect that $\bload{\cdot}$ would be the most suitable for general deployment or heterogeneous traffic patterns.
}

@@

\fakepara{Correspondence ratio}
the ratio between upstream and downstream traffic for a source IP.
We define this to be $C_X = \min(\mathit{up}, \mathit{down})/\max(\mathit{up}, \mathit{down})$, where a value close to 0 indicates strong asymmetry.

@@

All of the above features, save for global state, are 1-dimensional.
Each is tile-coded with 4 tilings and 6 tiles per dimension, using the windows described in \cref{tab:codings}.
We chose to take a separate tile-coding over each feature, ignoring combinatorial effects at present to minimise the amount of extra work an agent must perform.
Indeed, combining too many features into one tile-coding can lead to poor performance due to an inability to generalise action values across similar states.
On the other hand, treating each individually allows us to achieve a quick understanding of the importance of each while seeing adequate performance.

\Cref{fig:udp-feature-plots} shows the effectiveness of each for UDP (resp.\ \cref{fig:udp-feature-plots} for TCP), using a topology with $n=2$ hosts per egress point.
%?? Core findings---different protocols need different features, so everything we proposed above has a use!
The plots demonstrate that different protocols and traffic classes are best defended by different features---as such, every feature presented has value in a complete model.
In general, some of the most effective features are the global state, mean IAT, mean inbound packet size and $\Delta$ rates.
%?? How do they do when combined after individual training? Pretty well, especially for TCP.
Additional testing shows that the learned policies may be effectively combined (by summing action values), and are particularly effective for TCP; these results are omitted to preserve space.

%?? NEED TO SAY SOMEWHERE: Baselines use TC for establishing interleaving/buffers filling etc., when MARL+ or SPF are in play then disabling TC (thus allowing illegal states, with \num{-1} reward marking them as such---``negative reinforcement'') may accelerate learning. We have a choice---but the results show that for TCP we WANT TC enabled... For UDP, we actually get a slight degradation in performance. This suggests a kind of ``banding'', perhaps? Important to mention that it easily learns how to maintain a logical bandwidth limit.
During training of the above feature models, we elected to remove the physical bandwidth limit to allow agents to visit illegal states and receive \emph{negative reinforcement} for doing so.
It is important to note that this did not affect the agents' ability to keep the total load below $U_s$, as this behaviour can be easily learned in all cases.
%?? talk about cap difference: \cref{fig:tcp-cap-feature-plots}---we want cap enabled for TCP.
We found this led to a marginal improvement in efficacy when UDP was the primary source of benign traffic, but observed that this hindered learning when TCP was the primary protocol under protection (\cref{fig:tcp-cap-feature-plots})---likely due to the loss of key system dynamics.
It is anticipated that this difference might prove problematic for heterogeneous traffic mixtures one way of solving this may be to investigate the effect of replacing $U_s$ with e.g., $0.99 U_s$ in \cref{eqn:reward-but-better} to introduce a small band of negative reinforcement without actually removing the load restriction in the environment.
Our intent is to potentially accelerate learning while preserving the effects of system dynamics---we term these \emph{banded} rewards.

@@

?? They'd probably look real nice...

?? How to organise? by traffic type, or by model?

?? Probably best just to look at top level stuff, and THEN a simplified comparison for each intended improvement (like banded rewards).

@@

An \emph{indirect-control} RL problem, where the role played by the agents is to act in service to \emph{another technique} responsible for decision-making, further optimising or generalising aspects of its operation beyond that of hand-coded heuristics.
A past example includes learning when best to \emph{communicate} and share knowledge between \emph{hidden Markov model} anomaly detectors \cite{DBLP:conf/paisi/XuSH07}.
The position of this work is weakened by its reliance on the discredited `DARPA99' dataset \cite{DARPA-IDD, DBLP:conf/cisda/TavallaeeBLG09, DBLP:conf/sp/SommerP10}, but the idea itself is well-treated and this acts as a driver for improvements in this direction.
Outside of anomaly/intrusion detection, there has been growing interest in the use of reinforcement learning in data-driven networking, such as for intra-AS route optimisation \cite{DBLP:conf/hotnets/ValadarskySST17} and for resource-constrained process allocation \cite{DBLP:conf/hotnets/MaoAMK16}.
Work by \textcite{DBLP:conf/sigcomm/MaoNA17} employs client-side observations of network state and video player performance to optimise adaptive bitrate selection for multimedia streaming by RL methods.

@@

\subsection{Future Work}

@@

?? Can probably fold a lot of this out into discussion or something.

>>>>

\usepackage{etoolbox}
\usepackage[binary-units, per-mode=symbol]{siunitx}
\robustify\bfseries
\sisetup{detect-all, range-phrase=--, range-units=single, detect-weight=true,detect-inline-weight=math}

@@

\makeatletter\let\expandableinput\@@input\makeatother

@@

\newcommand{\arrload}[2]{\operatorname{load}^{#2}_{t}(#1)}
\newcommand{\uload}[1]{\arrload{#1}{\uparrow}}
\newcommand{\dload}[1]{\arrload{#1}{\downarrow}}
\newcommand{\bload}[1]{\arrload{#1}{\updownarrow}}
\newcommand{\cond}[2]{\operatorname{c}_{#1,t}#2}
%\fakepara{Reward function directionality}
The reward functions, as defined, do not take traffic direction into account.
We redefine these to identify overload states using both upstream and downstream loads, while allowing customisation of which direction is chosen for protection.
Denoting the upstream, downstream and combined loads $\uload{s}, \dload{s}, \bload{s}$, we modify \cref{eqn:reward}:
\begin{subequations}
\begin{gather}
\cond{f} = [\max(\uload{s}, \dload{s}) > U_s],\\
\cond{c}{(v)} = \cond{f}{} \cdot{} \, [\max(\uload{l_v}, \dload{l_v}) > U_s/k],
\end{gather}
\label{eqn:reward-but-better}
\end{subequations}
replacing $\arrload{t}{}$ in \crefrange{eqn:reward-rt}{eqn:reward-rctl} with whichever directional load is prioritised.
We choose $\uload{\cdot}$ for our UDP-based models and $\dload{\cdot}$ for HTTP, though we expect that $\bload{\cdot}$ would be the most suitable for general deployment or heterogeneous traffic patterns.

@@

\fakepara{Correspondence ratio}
the ratio between upstream and downstream traffic for a source IP.
We define this to be $C_X = \min(\uload{\cdot}, \dload{\cdot})/\max(\uload{\cdot}, \dload{\cdot})$, where a value close to 0 indicates strong asymmetry.

@@

All of the above features, save for global state, are 1-dimensional.
Each is tile-coded with 4 tilings and 6 tiles per dimension, using the windows described in \cref{tab:codings}.
We chose to take a separate tile-coding over each feature, ignoring combinatorial effects at present to minimise the amount of extra work an agent must perform.
Indeed, combining too many features into one tile-coding can lead to poor performance due to an inability to generalise action values across similar states.
On the other hand, treating features individually allows us to reach a quick understanding of the importance of each while seeing adequate performance.

\Cref{fig:udp-feature-plots} shows the effectiveness of each feature for UDP (resp.\ \cref{fig:udp-feature-plots} for TCP), using a topology with $n=2$ hosts per egress point.
%?? Core findings---different protocols need different features, so everything we proposed above has a use!
The plots demonstrate that different protocols and traffic classes are best defended by different features---as such, every feature presented has value in a complete model.
In general, some of the most effective features are the global state, mean IAT, mean inbound packet size and $\Delta$ rates.
%?? How do they do when combined after individual training? Pretty well, especially for TCP.
Additional testing shows that the learned per-feature policies may be easily combined (by summing action values), and that this technique is particularly effective for TCP; these results are omitted to preserve space.

%?? NEED TO SAY SOMEWHERE: Baselines use TC for establishing interleaving/buffers filling etc., when MARL+ or SPF are in play then disabling TC (thus allowing illegal states, with \num{-1} reward marking them as such---``negative reinforcement'') may accelerate learning. We have a choice---but the results show that for TCP we WANT TC enabled... For UDP, we actually get a slight degradation in performance. This suggests a kind of ``banding'', perhaps? Important to mention that it easily learns how to maintain a logical bandwidth limit.
During training of the above feature models, we elected to remove the physical bandwidth limit to allow agents to visit illegal states and receive \emph{negative reinforcement} for doing so.
It is important to note that this did not affect the agents' ability to keep the total load below $U_s$, as this behaviour can be easily learned in all cases.
%?? talk about cap difference: \cref{fig:tcp-cap-feature-plots}---we want cap enabled for TCP.
We found this led to a marginal improvement in efficacy when UDP was the primary source of benign traffic, but observed that this hindered learning when TCP was the primary protocol under protection (\cref{fig:tcp-cap-feature-plots}), likely due to the loss of key system dynamics.
It is anticipated that this difference might prove problematic for heterogeneous traffic mixtures.
One way of solving this may be to investigate the effect of replacing $U_s$ with e.g., $0.99 U_s$ in \cref{eqn:reward-but-better}, to introduce a small band of negative reinforcement without actually removing the load restriction in the environment.
Our intent is to potentially accelerate learning while preserving the effects of system dynamics---we term these \emph{banded} rewards.

@@

We now examine the performance of our two new models as compared against existing RL work under different traffic behaviour, for varying $n$.
%?? Probably best just to look at top level stuff, and THEN a simplified comparison for each intended improvement (like banded rewards).
Additionally, we examine the performance effects of environmental characteristics and potential improvements: negative reinforcement, the case where one agent makes all decisions, and pre-training on individual features.
We present the average rewards for all combinations of these factors in \cref{tab:av-vals}---these provide a rough idea of expected performance, giving the highest-performing model in bold.

Unless stated otherwise, these experiments use all \num{18} features introduced in \cref{sec:rethinking-the-state-space} (tile-coded individually), and make use of the physical bandwidth cap rather than pursuing negative reinforcement.
Test system specifications match those given in \cref{sec:performance-in-an-emulated-environment}.

\begin{table*}
	\centering
	\caption{Average reward for combinations of model, host density and traffic class.\label{tab:av-vals}}

	\expandableinput ../tables/big-avg-reward.tex
\end{table*}

\subsection{Congestion-unaware traffic}
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{../plots/udp-2}

	\caption{
		Online performance for $n=2$ hosts per egress point.
		\label{fig:udp-2}
	}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{../plots/udp-16}

	\caption{
		It's a thing.
		\label{fig:udp-16}
	}
\end{figure}

Yeah, Marl ++ is good. So what. \Crefrange{fig:udp-2}{fig:udp-16}

\subsection{Congestion-aware traffic}
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}

	\caption{
		It's a thing.
		\label{fig:tcp-2}
	}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{../plots/tcp-16}

	\caption{
		It's a thing.
		\label{fig:tcp-16}
	}
\end{figure}

Yeah, Marl ++ is still good. So what. \Crefrange{fig:tcp-2}{fig:tcp-16}

\subsection{Banded rewards and negative reinforcement}

?? Generally? Not good.
?? While uncapped led to a per-feature improvement for UDP, Uncapped worse in all cases when all features included.

\subsection{Single-agent performance}

?? Curiously, MARL suffers but SPF actually become usable.

\subsection{Per-feature training}

?? Not yet performed.

?? Most importantly this still trails behind existing (exact) DDoS flow detection mechanisms

@@

An \emph{indirect-control} RL problem is one where the role played by the agents is to act in service to \emph{another technique} responsible for decision-making, further optimising or generalising aspects of its operation beyond that of hand-coded heuristics.
A past example includes learning when best to \emph{communicate} and share knowledge between \emph{hidden Markov model} anomaly detectors \cite{DBLP:conf/paisi/XuSH07}.
The position of this work is weakened by its reliance on the discredited `DARPA99' dataset \cite{DARPA-IDD, DBLP:conf/cisda/TavallaeeBLG09, DBLP:conf/sp/SommerP10}, but the idea itself is well-treated and this acts as a driver for improvements in this direction.
Outside of anomaly/intrusion detection, there has been growing interest in the use of reinforcement learning in data-driven networking, such as for intra-AS route optimisation \cite{DBLP:conf/hotnets/ValadarskySST17} and for resource-constrained process allocation \cite{DBLP:conf/hotnets/MaoAMK16}.
Work by \textcite{DBLP:conf/sigcomm/MaoNA17} employs client-side observations of network state and video player performance to optimise adaptive bitrate selection for multimedia streaming by RL methods.

@@

\section{Future Work}

@@
